Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-01 doc/PRF2022/PRF_main.tex
updated manuscript

Once \eqref{eq:stokes}-\eqref{eq:force} have been solved,
the velocities $(\vv_i, \omega_i)$ from \eqref{eq:rigid-vel}
update the particle positions and orientations.
We use the parameters $\mu = 1$ cP, $\gamma = 4$ pN nm$^{-1}$,
$\rho = 5$ nm, $c = 1.25$ nm, $M = 2$ pN, and $\rho_0 = 0.5$ nm.
These values give a characteristic time $1$ ns and characteristic length $1$ nm.

@@

In terms of fluid behavior,
the multilamellar (BC (ii)) structure behaves as shear thinning fluid
while the striated structure (BC (iii)) has a finite yield stress. 
Qualitatively, the strains for BC (ii) increases gradually 
with shear rate (Fig~\ref{fig:BC2_shear}(f)).
In contrast, the strains for BC (iii) are constant over a range of flow strengths
and then increase when the flow strengths are large enough
to deform the body (Fig~\ref{fig:BC3_shear}(f)).
To quantify this behavior, we form 
\[
\mu_{\text{sus}} = \frac{\dot \gamma}{\dot E} \mu
\]
as an effective dynamic viscosity of the suspension.
The numerator $\dot \gamma \mu$ gives the force per area provided by the solvent stresses. 
The strain rate $\dot E$ of the body is the slope of a linear fit to the strain curves e.g.,
in Fig~\ref{fig:BC2_shear}(f).

Calculated suspension viscosities are shown
in Table \ref{tbl:bcii_visc}.
The middle row gives the solid area fraction $\phi$;
the sum of the rigid particle areas divided by the
total area of the solvent and particle region.
We observe that for the multilamellar structure,
$\mu_{\text{sus}}$ is decreasing
with increasing shear rate.
The predicted suspension viscosities 
are on the order of hundreds of times that of water,
consistent with measurements of noninteracting
particle suspensions\cite{KONIJN201461}.
In the case of striated structures, viscosity is
effectively infinite for the lower two of the shear rates,
and then drops to a finite value $\mu_{\text{sus}} = 60$ mPa s
when the shear rate reaches $0.15$ ns$^{-1}$.
\begin{table}
  \caption{Suspension viscosity $\mu_{\text{sus}}$ (mPa s) 
\label{tbl:bcii_visc}
}
\centering
\begin{tabularx}{0.7\textwidth}{c|X|X|X||X|X|X}
&\multicolumn{3}{c||}{BC (ii)} & \multicolumn{3}{c}{BC (iii)}\\
\hline
  $\dot \gamma$ & 0.05 & 0.10 \quad & 0.15 & 0.100 & 0.125 & 0.15\\
  \hline
  $\phi$ & 0.50 & 0.47 & 0.41 & 0.47 & 0.46 & 0.45 \\
  \hline
  $\mu_{\text{sus}} $ & 401 & 66 & 42 & 2.5e3 & 1.4e3 & 60\\
\hline
\end{tabularx}
\end{table}

We have not calculated suspension viscosities for the type (i) boundary condition,
because the viscosities of bilayer are in-plane and require fully three-dimensional
simulations to resolve\cite{denOtter2007,Zgorski2019,doi:10.1073/pnas.2100156118}.  Our previous work 
did calculate, however, an intermonolayer friction coefficient $b$
which is related but conceptually different than viscosity \cite{Fu2022_JFM}.

>>>>

Once \eqref{eq:stokes}-\eqref{eq:force} have been solved,
the velocities $(\vv_i, \omega_i)$ from \eqref{eq:rigid-vel}
update the particle positions and orientations.
We use the parameters $\mu = 1$ mPa s, $\gamma = 4$ pN nm$^{-1}$,
$\rho = 5$ nm, $c = 1.25$ nm, $M = 2$ pN, and $\rho_0 = 0.5$ nm.
These values give a characteristic time $1$ ns and characteristic length $1$ nm.

@@

In terms of fluid behavior,
the multilamellar (BC (ii)) structure behaves as shear thinning fluid
while the striated structure (BC (iii)) has a finite yield stress. 
Qualitatively, the strains for BC (ii) increases gradually 
with shear rate (Fig~\ref{fig:BC2_shear}(f)).
In contrast, the strains for BC (iii) are constant over a range of flow strengths
and then increase when the flow strengths are large enough
to deform the body (Fig~\ref{fig:BC3_shear}(f)).
To quantify this behavior, we form 
\[
\mu_{\text{hyd}} = \frac{\dot \gamma}{\dot E} \mu
\]
as an effective dynamic viscosity of the particle assemblies.
The numerator $\dot \gamma \mu$ gives the force per
area provided by the solvent stresses where
$\mu = 1$ mPa s is
the solvent viscosity.
The strain rate $\dot E$ of the body is the slope of a linear fit to the strain curves e.g.,
in Fig~\ref{fig:BC2_shear}(f).

Calculated viscosities of particle assemblies are shown
in Table \ref{tbl:bcii_visc}.
The middle row gives the solid area fraction $\phi$;
the sum of the rigid particle areas divided by the
total area of the solvent and particle region.
We observe that for the multilamellar structure,
$\mu_{\text{hyd}}$ decreases
with increasing shear rate.
The predicted viscosities of the particle assemblies
are on the order of hundreds of times that of water,
consistent with suspension viscosities for noninteracting
particles \cite{KONIJN201461}.
In the case of striated structures, viscosity is
effectively infinite for the lower two of the shear rates,
and then drops to a finite value $\mu_{\text{hyd}} = 60$ mPa s
when the shear rate reaches $0.15$ ns$^{-1}$.
\begin{table}
  \caption{Dynamic viscosity of assemblies $\mu_{\text{hyd}}$ (mPa s) 
\label{tbl:bcii_visc}
}
\centering
\begin{tabularx}{0.7\textwidth}{c|X|X|X||X|X|X}
&\multicolumn{3}{c||}{BC (ii)} & \multicolumn{3}{c}{BC (iii)}\\
\hline
  $\dot \gamma$ & 0.05 & 0.10 \quad & 0.15 & 0.100 & 0.125 & 0.15\\
  \hline
  $\phi$ & 0.50 & 0.47 & 0.41 & 0.47 & 0.46 & 0.45 \\
  \hline
  $\mu_{\text{sus}} $ & 401 & 66 & 42 & 2.5e3 & 1.4e3 & 60\\
\hline
\end{tabularx}
\end{table}

In the case of BC (i), our previous work\cite{Fu2022_JFM} calculated a
friction coefficient $b$ for the intermonolayer slip between the two leaflets
of a bilayer. \citet{denOtter2007,Zgorski2019} and
\citet{doi:10.1073/pnas.2100156118} have
calculated in-plane viscosities for fully three-dimensional bilayers.
Although not part of this work,
it is in principle possible to obtain an in-plane
viscosity using the hydrophobic potential
\eqref{eq:free_energy}
by replacing the boundary condition \eqref{eq:bc-type}
with one that is everywhere constant, in effect modeling
lipids in a bilayer as an array of as elongated, purely hydrophobic pilars.
